Curve Average \\ {\large Project 3 for class CS6491 Computer Graphics}

### 2015-11-02 paper/paper.tex
Wrote the algorithms and the block diagram. Next: Fill in the text

\usepackage[english]{babel}
%\usepackage[latin1]{inputenc}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{tikz}
\usepackage{verbatim}
\usepackage{subcaption}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage[pdftex]{hyperref}

\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmiccomment}[1]{\ \ // #1} % C-like // Comments

@@

\section{Average Curve Computation}\label{chapter:Tracing}

\subsection{Distance functions}
TODO

\subsection{Curve tracing}
TODO

@@

\section{Visualization and Editing}\label{chapter:Visual}

>>>>

\usepackage{blindtext}
\usepackage[english]{babel}
%\usepackage[latin1]{inputenc}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{tikz}
\usepackage{verbatim}
\usepackage{subcaption}
% \usepackage{algorithm}
% \usepackage{algorithmic}
\usepackage[pdftex]{hyperref}
\usepackage[algoruled, vlined,linesnumbered]{algorithm2e}

\usepackage{tikz}
\usetikzlibrary{shapes,arrows}
\tikzstyle{block} = [draw, fill=blue!20, rectangle, 
    minimum height=3em, minimum width=6em]
\tikzstyle{sum} = [draw, fill=blue!20, circle, node distance=1cm]
\tikzstyle{input} = [coordinate]
\tikzstyle{output} = [coordinate]
\tikzstyle{pinstyle} = [pin edge={to-,thin,black}]
% \renewcommand{\algorithmicrequire}{\textbf{Input:}}
% \renewcommand{\algorithmiccomment}[1]{\ \ // #1} % C-like // Comments

@@

\newpage
\section{Average Curve Computation}\label{chapter:Tracing}

\begin{figure*}
 \centering
% The block diagram code is probably more verbose than necessary
\begin{tikzpicture}[auto, node distance=2cm,>=latex']
    \node [block, align=center] (traceCurve) {traceCurve\\\scriptsize Algorithm 2};
    \node [block, right of=traceCurve, align=center, node distance=3cm] (snap) {snap\\\scriptsize Algorithm 3};
    \draw [draw,->] (traceCurve) -- (snap);
    \node [block, right of=snap, align=center, node distance=3cm] (findClosest) {findClosest};
    \draw [->] (snap) -- (findClosest);
    \node [block, right of=findClosest, align=center, node distance=3cm] (closestOnCubicHermite) {cubicHermite\\ \scriptsize Algorithm 1};
    \draw [->] (findClosest) -- (closestOnCubicHermite);
    \node [block, right of=closestOnCubicHermite, node distance=3cm] (solveQuintic) {solveQuintic};
    \draw [->] (closestOnCubicHermite) -- (solveQuintic);
    \node [block, right of=solveQuintic, node distance=3cm] (Laguerre) {Laguerre};
    \draw [->] (solveQuintic) -- (Laguerre);
    \node [block, below of=closestOnCubicHermite, align=center] (quadraticHermite) {quadraticHermite};
    \draw [->] (findClosest) |- (quadraticHermite);
    \node [block, right of=quadraticHermite, node distance=3cm] (solveCubic) {solveCubic};
    \draw [->] (quadraticHermite) -- (solveCubic);
\end{tikzpicture}
\normalsize 
\caption{\normalsize Block diagram for the major functions involved in tracing the average curve}
\end{figure*}

\subsection{Distance functions}
TODO
\blindtext

\subsubsection{Newton-Raphson Method}
TODO
\blindtext

\subsubsection{Laguerre's Method}
TODO
\blindtext
\SetArgSty{textup}
\begin{algorithm}[ht!]
  \SetCommentSty{emph}
  \KwIn{$\{P_0, T_0, P_1, T_1\}$: control points, $Q$: input point}
  \KwResult{$t$: time in $[0,1]$ for the closest point}
  $[a,b,c,d,e,f] \leftarrow $generateDistanceCoeffs$(P_0,T_0,P_1,T_1,Q)$; \\
  $res \leftarrow $solveQuintic($a,b,c,d,e,f$); \\
  $\{minDist, t^*\} \leftarrow \{\infty,-1\}$;\\
  \ForEach{$r \in res$} {
    \lIf{$|r.im| > 0$} \textbf{continue}; \\
    \lIf{$r.re < 0\;$ \textbf{or} $\;r.re > 1$} \textbf{continue}; \\
    $P_t \leftarrow \tau(P_0,T_0,P_1,T_1,r.re)$; \\
    \If{$|P_t - Q| < minDist$} {
      $\{minDist, t^*\} \leftarrow \{|P_t - Q|, r.re\}$;\\
    }
  }
  \Return{$t^*$};
  \caption{closestPointOnCubicHermite()}
\end{algorithm}

\subsection{Curve tracing}
TODO
\blindtext

\begin{algorithm}[ht!]
  \SetCommentSty{emph}
  \KwIn{$\{\mathbf{A},\mathbf{B}\}$: curves}
  \KwResult{$\mathbf{C}$: average curve}
  $\mathbf{C}.$add($\mathbf{A}[0], 0$); \\
  $\{current, t_a, t_b, t_a^\prime, t_b^\prime\} \leftarrow \{\mathbf{C}[0],0,0,0,0\}$; \\
  \While{true} {
  $\vec{T}_A \leftarrow \vec{n}$($\mathbf{A}.\tau$($min(1,t_a+\epsilon)$) - $\mathbf{A}.\tau$($min(1,t_a)$)); \\
  $\vec{T}_B \leftarrow \vec{n}$($\mathbf{B}.\tau$($min(1,t_b+\epsilon)$) - $\mathbf{B}.\tau$($min(1,t_b)$)); \\
  $current \stackrel{+}\leftarrow \text{STEP\_SIZE} \;\vec{n}(\vec{T}_A + \vec{T}_B)$; \\
  $\{t_a^\prime, t_b^\prime, r, P_c\} \leftarrow \text{snap}(\mathbf{A},\mathbf{B},current)$; \\
  \lIf{$max(t_a,t_b) < 1$ \textbf{or} $t_a^\prime < t_a$ \textbf{or} $t_b^\prime < t_b$} \textbf{break}; \\
  $\mathbf{C}.$add($P_c$); \\
  }
  \Return{$\mathbf{C}$};
  \caption{traceCurve()}
\end{algorithm}

TODO
\blindtext

\begin{algorithm}[ht!]
  \SetCommentSty{emph}
  \KwIn{$\{\mathbf{A},\mathbf{B}\}$: curves, $Q:$ input point}
  \KwResult{$\{t_a,t_b\}$: projections, $\{P_c, r\}$: sphere center/radius}
  $P_c \leftarrow Q$; \\
  \While{$i\texttt{++} < \;$MAX\_ITERS } {
    $\{P_A, \vec{T}_A, r_A, t_A\} \leftarrow $closestPoint$(\mathbf{A}, P_c)$;  \\
    $\{P_B, \vec{T}_B, r_B, t_B\} \leftarrow $closestPoint$(\mathbf{B}, P_c)$;  \\
    $error \leftarrow |P_A - P_c| - |P_B - P_c|;$\\ 
    \lIf{$error < \epsilon$} \textbf{break;} \\
    $P_c \leftarrow P_c - error \;\vec{n}(\vec{T}_A - \vec{T}_B);$ \\
    $\{d_A, \vec{V}_A\} \leftarrow $planeDist($P_c, P_A, P_B, \mathbf{A}.\tau(t_A + \epsilon))$;\\
    $\{d_B, \vec{V}_B\} \leftarrow $planeDist($P_c, P_B, P_A, \mathbf{B}.\tau(t_B + \epsilon))$;\\
    $P_c \leftarrow P_c - \text{PLANE\_PROJ\_COEFF} \;(d_A \vec{V}_A + d_B \vec{V}_B); $\\
  }
  \Return{$\{c_A.t, c_B.t, P_c, c_A.r\}$};
  \caption{snap()}
\end{algorithm}

@@

\newpage
\section{Visualization and Editing}\label{chapter:Visual}
